# Week 3 Short Answer Questions

## Corey McGinnis

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

##5.1
```{r}
ggplot(data=CPS85,aes(x=sex,y=wage ))+geom_bar(stat='identity',position='stack', width=.9)+ facet_wrap(~south,ncol=3) 
```

#5.2
```{r}
WorldMap(HappinessIndex,country,corruption)
```

#6.5
b. State and Polling Organization

#6.6
d. Glyph: Rectangle. Graphical attribute: color and text

#6.7
d. NYT poll probability for the Democratic Candidate

#6.8
```{r}
Small <-
  NCHS %>%
  sample_n(size = 5000)

ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker) 
```

x-coord maps to bmi
y-coord maps to weight
color blue maps to smoker
color red maps to non-smoker
color grey maps to NA

#7.1, 
a. mean
b. mutate
c. desc
d. filter
e. group_by
f. summarise

#7.4
a) Uses a case not a variable in group_by
b) Calls Tmp in summarize
c) doesn't use %>%

#7.5, 
a) arrange(count)
```{r}
BabyNames %>%
  arrange(count)
```
b) filter(sex == "F")
c) filter(sex == "M")
d) summarise(total = sum(count))
e) group_by(name, count)
#7.7, 
a) do not need to use BabyNames in groupby or summarise
b) never calls BabyNames
c) uses -> instead of %>%
d) statements and syntax are backwards

#7.11, 
a. number of patients of each sex and their average age
b. number of patients with each diagnosis, and the mean age of each diagnosis
c. number of patients with each diagnosis divided into the different sexes, mean age of each sex diagnosis
d. number of types of diagnosises at each age, average age of each age
e. number of people at each different age, and average age
#7.12
1. n()
2. names
3. ??
4. library
5. group_by
6. sum