# Week 4 Short Answer Questions

## Corey McGinnis

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

#8.1, 
1) c)
2) a), b), g)
3) e)
4) f)
5) d)

#8.2, 
(1) ggplot(CPS85, aes(age, wage)) + geom_point(aes(shape = married)) + facet_wrap(~sector)
(2) ggplot(CPS85, aes(age, wage)) + geom_point(aes()) + facet_wrap(~married~sex)

#8.3
(A) ggplot(CPS85, aes(age, wage)) + geom_point(aes())
(B) ggplot(CPS85, aes(age, wage)) + geom_point(aes(shape = sex))
(C) ggplot(CPS85, aes(age, wage)) + geom_point(aes(shape = sex)) + facet_wrap(~married)
(D) ggplot(CPS85, aes(age, wage)) + geom_point(aes(shape = married))

#9.1, 
a) transformation
b)data verb
c)
d)summary
e)
f)summary function
g)summary function
h)data verb
i)quick presentation

#9.3
1.
```{r}
library(ggplot2)
```

```{r}
diamonds %>%
  group_by(color) %>%
  summarise(weight = mean(carat)) %>%
  arrange(desc(weight)) %>%
  head(1)
```
J

2.
```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(size = mean(table/carat)) %>%
  arrange(desc(size)) %>%
  head(1)
```
VVS1
