# Week 2 Project

## Corey McGinnis

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

I downloaded these data from the following site: "http://tiny.cc/dcf/Library-small.rda"

#Basics

```{r}
load("~/Comp-110-Assignments-Spring-2017/Library-small.rda")
```


4.
Number of cases in `Bks`
```{r}
nrow(Bks)
```


Names of variables in `Bks`
```{r}
names(Bks)
```


Number of cases in `Inv`
```{r}
nrow(Inv)
```


Names of variables in `Inv`
```{r}
names(Inv)
```


5. The number of books with each different `Current.Status`
```{r}
Inv %>%
  group_by(Current.Status) %>%
  tally()
```
1866 books are available, 
1 book is missing,
18 books are on loan,
and 115 books are withdrawn

6. Number of times books have been checked out
```{r}
Inv %>%
  group_by(Issued.Count) %>%
  tally()
```
There are
996 books that have been checked out 0 times,
337 books that have been checked out 1 time,
203 books that have been checked out 2 times,
121 books that have been checked out 3 times,
69 books that have been checked out 4 times,
46 books that have been checked out 5 times,
38 books that have been checked out 6 times,
29 books that have been checked out 7 times,
24 books that have been checked out 8 times,
20 books that have been checked out 9 times,
and an unidentified number of books that have been checked out 10 or more times.
