# Week 2 Short Answer Questions

## Corey McGinnis

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

1.1
a) Taffy: value
b) year: quantitative
c) sex: categorical
d) name: categorical
e) count: quantitative

1.2
-first value of president written "Lincoln, Abraham", not conforming with the "First Last" format
-third value of in office written 1837 to 1841, not conforming to startyear-endyear format
-first value in number of states written "it depends" rather than being a number

1.4
A: year (year), Algeria (value), Brazil (value), Columbia (value)
B: Country (country), y2000 (value), y2001 (value)
C: Country (country), year (year), value (value)

1.5
5 variables
The cases represent different bits of data about each variable
I did not understand the difference between numerical and quantitative


2.2
file name
the name of an argument in a named argument

2.3
Current Population Survey

2.4
The NHANES, at the beginning is unneccesary

2.6
first-essay contains subtraction sign
"MyData" is a string
small sample contains a space
.MyData. starts with a dot
sqrt() is already a function

2.7


2.8
a. improper syntax (no parentheses)
b. improper syntax (two dashes)
c. invalid object name
d. missing end quotation
e. no mistake

2.9
. and _ can be used in R object
all can be used in a character string

2.10
CountryData has 76 variables
tfat measures mass of trunk fat
23018 cases in WorldCities
count is the third variable in BabyNames
Party affiliation: DEM=Democratic, LIB=Libertarian,REP=Republican,UNA=Unaffiliated

```{r}
data("CountryData")
View(CountryData)
```


3.1
1. data frame
2. fireplace = function(x) {return(x)}
3. name = "fireplace"
4. fireplace = 10

3.2
should be filter(name=="Prince")

3.3
should be help(NHANES)

3.4
BabyNames = data table name
filter = function
name = variable name
== = function name
group_by = function
year = name of a named argument
sex - name of a named argument
summarise = function
yearlyTotal = variable
sum = function
count = name of a named argument
ggplot = function
aes = function
x = variable
y = variable
geom_pont = function
color = variable
geom_vline = function
xintercept = variable

3.5

brain weight
56 cases
it exists/ we have data
herbi, omni, carni, insecti: what they eat

3.6
```{r}
BabyNames %>%
  group_by(year, sex) %>%
  summarise(totalBirths=sum(count))
```