# Week 3 Project

## Corey McGinnis

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

###Deconstructing graphics

1) Scatter plot 
variables: exper, wage, sector, married
role: exper on x-axis, wage on y-axis, color by married, faceted by sector

2) Density plot
variables: bmi, sex, pregnant
role: bmi on x axis, color by sex, faceted by pregnant
No data variable for y-axis because it is a density plot: measures number of cases on x-axis

```{r}
ggplot(data = CPS85, aes(x =  exper, y = wage, color = married)) + geom_point() + facet_wrap( ~ sector)
ggplot(data = NCHS, aes(x = bmi, fill = TRUE, alpha = .01)) + geom_density(aes(color = sex)) + facet_wrap(~ pregnant)
```

###Wrangling

1.
```{r}
diamonds %>% 
  group_by( color ) %>% 
  summarise( size = mean(carat) ) %>% 
  arrange(desc( size )) %>% 
  head( 1 )
```

2.
```{r}
diamonds %>% 
  group_by( clarity ) %>% 
  summarise( size = mean(table) ) %>%
  arrange(desc( size )) %>% 
  head( 1 )
```

####Voting

1. cases
```{r}
tally(Minneapolis2013)
```

2. top 5 candidates
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(votes = n()) %>%
  arrange(desc(votes)) %>%
  head(5)
```

3.
```{r}
Minneapolis2013 %>%
  filter(First == "undervote") %>%
  summarise(total1st = n())

Minneapolis2013 %>%
  filter(Second == "undervote") %>%
  summarise(total2nd = n())

Minneapolis2013 %>%
  filter(Third == "undervote") %>%
  summarise(total3rd = n())
```

4.
```{r}
Minneapolis2013 %>%
  filter(First == "BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(votes = n()) %>%
  arrange(desc(votes)) %>%
  head(3)
```

5.
```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(fraction = mean(First == "undervote")) %>%
  arrange(desc(fraction)) %>%
  head(1)
```

