# Week 6 Project

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r cache=TRUE}
data_site <- 
  "http://tiny.cc/dcf/2014-Q4-Trips-History-Data-Small.rds" 
Trips <- readRDS(gzcon(url(data_site)))
```

```{r}
names(Trips)
head(Trips)
```


1. A density plot of the events verus sdate
```{r}
Trips %>%
  ggplot(aes(x = sdate)) + geom_density(bw=100000)
```
2. 
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) + lubridate::minute(sdate) / 60) %>%
  ggplot(aes(x = time_of_day)) + geom_density()
  
```

3.
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) + lubridate::minute(sdate) / 60) %>%
  mutate(day_of_week = lubridate::wday(sdate)) %>%
  ggplot(aes(x = time_of_day)) + geom_density() + facet_wrap(~day_of_week)
```

4.
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) + lubridate::minute(sdate) / 60) %>%
  mutate(day_of_week = lubridate::wday(sdate)) %>%
  ggplot(aes(x = time_of_day)) + geom_density(aes(fill=client), alpha = 0.5) + facet_wrap(~day_of_week)
```

5.
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) + lubridate::minute(sdate) / 60) %>%
  mutate(day_of_week = lubridate::wday(sdate)) %>%
  ggplot(aes(x = time_of_day)) + geom_density(aes(fill=client), alpha = 0.5, position = position_stack()) + facet_wrap(~day_of_week)
```
This first choice tells you a more interesting story because it is clearer when casual are riding, and when casual are riding. You see each peak individually

6.
facet on wday, fill with client
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) + lubridate::minute(sdate) / 60) %>%
  mutate(wday = ifelse(lubridate::wday(sdate) %in% c(1,7), "weekend", "weekday")) %>%
  ggplot(aes(x = time_of_day)) + geom_density(aes(fill=client), alpha = 0.5) + facet_wrap(~wday)
```

facet on client, fill with wday
```{r}
Trips %>% 
  mutate(time_of_day = lubridate::hour(sdate) + lubridate::minute(sdate) / 60) %>%
  mutate(wday = ifelse(lubridate::wday(sdate) %in% c(1,7), "weekend", "weekday")) %>%
  ggplot(aes(x = time_of_day)) + geom_density(aes(fill=wday), alpha = 0.5) + facet_wrap(~client)
```
Both are useful because we can see that registered users have a very similar pattern to weekday users, and casual to weekend users. Both however, tell nearly the same story.